Article Title

### 2013-11-01 sections/Results.tex
changes in response to Kreso's comments this morning: wording in the Results section.

\subsection*{Covariance estimation}
We aim to estimate the true covariance matrix 
\begin{equation}
\Sigma = \E{(x-\mu)(x-\mu)^\T}
\end{equation}
where $\E{\cdot}$ denotes expectation  and $x$ is the $p\times 1$ vector of real-valued instantaneous firing rates discretized into bins of duration $\Delta t$ and $\mu = \E{x}$.

@@

The sample covariance matrix is unbiased i.e.\;$\E{\hat\Sigma_0}-\Sigma=0$.  For finite sample sizes, however, $\hat\Sigma_0$ is not as close to $\Sigma$ as a number of biased estimators that rely on \emph{regularization}. Regularization is the deliberate biasing of the estimate toward a low-dimensional, less variable \emph{target estimate} to strike a favorable balance between bias and variability of the estimate \cite{Bickel:2006,Ledoit:2004}.  The estimator whose target estimate most closely matches the true low-dimensional structure of the data is likely to outperform other estimators.

@@

In the first regularized estimator, the target estimate is a diagonal matrix $\hat D$.  The optimized estimate $\hat\Sigma_{\rm diag}$ is obtained by the linear \emph{shrinkage} of the unbiased estimate $\hat\Sigma_0$ toward $\hat D$ as regulated by scalar \emph{shrinkage intensity} $\lambda \in [0, 1]$:
\begin{equation}
\hat \Sigma_{\sf diag} = (1-\lambda) \hat \Sigma_0 + \lambda \hat D
\end{equation}
The diagonal target estimate expresses the idea of lack of dependence (or of linear association) between the activity of observed neurons (Fig.~\ref{fig:03}A).  If this assumption aptly describes recorded data, then strong shrinkage toward $\hat D$ will add little bias while strongly reducing the variability of the estimate.

@@

The third estimator is based on the assumption that all correlations are the result of direct linear interactions between a fraction of observed cell pairs.  This assumption is enforced by reducing to zero the majority of pairwise \emph{partial correlations} in the recorded population. While usual correlations are calculated from the marginal distribution without conditioning on all the other neurons, the partial correlation expresses the pairwise correlation conditioned on the activity of all the other cells.  If cells only exert linear effects on each other and all neurons are visible, partial correlations express the direct interactions between neurons. Therefore, this estimator is biased toward the assumption that correlations arise due to interactions between a subset of pairs of recorded neurons (Fig.~\ref{fig:03}C). When the partial correlation between a pair of neurons is zero, then the corresponding element of the inverse of the covariance matrix (often referred to as the \emph{precision matrix} or \emph{concentration matrix}) must be zero as well. Then the estimator is 
\begin{equation}
\hat\Sigma_{\sf sparse} = \hat S^{-1}
\end{equation}
where $\hat S$ is a sparse matrix with a large fraction of zeros in its off-diagonal elements. The  one hyperparameter $\rho$ expresses the sparsity (fraction of off-diagonal zeros) in $\hat\Sigma$.

>>>>

\subsection*{Covariance estimation}
We aim to estimate the true covariance matrix 
\begin{equation}
\Sigma = \E{(x-\mu)(x-\mu)^\T}
\end{equation}
where $\E{\cdot}$ denotes expectation; $x$ is the $p\times 1$ vector of real-valued instantaneous firing rates in bins of duration $\Delta t$. The vector of mean firing rates is $\mu = \E{x}$.

@@

The sample covariance matrix is unbiased i.e.\;$\E{\hat\Sigma_0}-\Sigma=0$.  For finite sample sizes, however, $\hat\Sigma_0$ is not as close to $\Sigma$ as a number of biased estimators that rely on \emph{regularization}. Regularization is the deliberate biasing of the estimate toward a low-dimensional, less variable \emph{target estimate} to strike a favorable balance between bias and variability of the estimate \cite{Bickel:2006,Ledoit:2004}.

The estimator whose target estimate most closely matches the true low-dimensional structure of the data is likely to outperform other estimators. This principle provides the logic of this study.

@@

In the first regularized estimator, the target estimate is the diagonal matrix $\hat D$ containing on its diagonal estimates of the variances for each neuron.  The optimized estimate $\hat\Sigma_{\rm diag}$ is obtained by the linear \emph{shrinkage} of the unbiased estimate $\hat\Sigma_0$ toward $\hat D$ as regulated by scalar \emph{shrinkage intensity} $\lambda \in [0, 1]$:
\begin{equation}
\hat \Sigma_{\sf diag} = (1-\lambda) \hat \Sigma_0 + \lambda \hat D
\end{equation}
The diagonal target estimate expresses the idea of lack of dependence (or of linear association) between the activity of observed neurons (Fig.~\ref{fig:03}A).  If this assumption aptly describes recorded data, then strong shrinkage toward $\hat D$ will add little bias while strongly reducing the variability of the estimate.

@@

The third estimator is based on the assumption that all correlations are the result of direct linear interactions between a fraction of observed cell pairs.  This assumption is enforced by reducing to zero the majority of pairwise \emph{partial correlations} in the recorded population. While usual correlations are calculated from the marginal distribution without conditioning on all the other neurons, the partial correlation expresses the pairwise correlation conditioned on the activity of all the other cells.  If cells only exert linear effects on each other and all neurons are visible, partial correlations express the direct interactions between neurons. Therefore, this estimator is biased toward the assumption that correlations arise due to interactions between a subset of pairs of recorded neurons (Fig.~\ref{fig:03}C). When the partial correlation between a pair of neurons is zero, then the corresponding element of the inverse of the covariance matrix (often referred to as the \emph{precision matrix} or \emph{concentration matrix}) must be zero as well. Then the estimator is 
\begin{equation}
\hat\Sigma_{\sf sparse} = \hat S^{-1}
\end{equation}
where $\hat S$ is a sparse matrix with a large fraction of zeros in its off-diagonal elements. The estimate has one hyperparameter to regulate the sparsity (fraction of off-diagonal zeros) in $\hat\Sigma$.
